---
title: "MKTG 562 ASSGN PRICING"
author: "Naga Soundari Balamurugan"
date: "14 October 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let us first import the data into the markdown
```{r}
data = read.csv('./Ex3_Data_R.csv')
attach(data)
```

First let us run the analysis for the first App

Linear model for App 1
```{r}
y = UNITS1
x1 = REGPR1
x2 = FEAT1
x3 = RATING1

# Generating a linear model
# Run the Regression (includes an INTERCEPT)
linear.app1 <- lm(y ~ x1 + x2 + x3, data = data)
summary(linear.app1)

```

Analysis:
To interpret the results of the regression coefficients, let us first find the mean values of Sales, Price, Rating and Feature

```{r}
mean.price.app1 = mean(REGPR1)
mean.feat.app1 = mean(FEAT1)
mean.rating.app1 = mean(RATING1)
mean.sales.app1 = mean(UNITS1)

# Now let us find the coefficient for comparing effect of each feature
(coeff.price.1 = (linear.app1$coefficients[2])*(mean.price.app1)/(mean.sales.app1))

(coeff.feat.1 = (linear.app1$coefficients[3])*(mean.feat.app1)/(mean.sales.app1))

(coeff.rating.1 = linear.app1$coefficients[4]*(mean.rating.app1)/(mean.sales.app1))

```





First let us run the analysis for the first App

Semi Log model for App 1
```{r}
y = log(UNITS1)
x1 = REGPR1
x2 = FEAT1
x3 = RATING1

# Generating a semi log model
# Run the Regression (includes an INTERCEPT)
semilog.app1 <- lm(y ~ x1 + x2 + x3, data = data)
summary(semilog.app1)
```
Interpreting the analysis of semi log model
Analysis:
To interpret the results of the regression coefficients, let us first find the mean values of Sales, Price, Rating and Feature

```{r}
mean.price.app1 = mean(REGPR1)
mean.feat.app1 = mean(FEAT1)
mean.rating.app1 = mean(RATING1)
mean.sales.app1 = mean(UNITS1)

# Now let us find the coefficient for comparing effect of each feature
(coeff.price.1 = (semilog.app1$coefficients[2])*(mean.price.app1))

(coeff.feat.1 = (semilog.app1$coefficients[3])*(mean.feat.app1))

(coeff.rating.1 = semilog.app1$coefficients[4]*(mean.rating.app1))

```



First let us run the analysis for the first App

Complete Log model for App 1
```{r}
y = log(UNITS1)
x1 = log(REGPR1)
x2 = FEAT1
x3 = log(RATING1)

# Generating a complete log model
# Run the Regression (includes an INTERCEPT)
log.app1 <- lm(y ~ x1 + x2 + x3, data = data)
summary(log.app1)
```