---
title: "MKTG_Ex_3"
author: "Naga Soundari Balamurugan"
date: "October 14, 2018"
output: pdf_document
---

```{r Read data, include=FALSE}
appSalesData <- read.csv("Ex3_Data_R.csv")

```


```{r log, include=FALSE}
#App1
appSalesData$LogUNITS1 <- log(appSalesData$UNITS1)
appSalesData$LogREGPR1 <- log(appSalesData$REGPR1)

#App2
appSalesData$LogUNITS2 <- log(appSalesData$UNITS2)
appSalesData$LogREGPR2 <- log(appSalesData$REGPR2)

#App3
appSalesData$LogUNITS3 <- log(appSalesData$UNITS3)
appSalesData$LogREGPR3 <- log(appSalesData$REGPR3)


####################### Mean values for Coefficients Comparison ################################
meanPriceApp1 <- mean(appSalesData$REGPR1)
meanFeatApp1 <- mean(appSalesData$FEAT1)
meanSalesApp1 <- mean(appSalesData$UNITS1)
meanRatingApp1 <- mean(appSalesData$RATING1)

meanPriceApp2 <- mean(appSalesData$REGPR2)
meanFeatApp2 <- mean(appSalesData$FEAT2)
meanSalesApp2 <- mean(appSalesData$UNITS2)
meanRatingApp2 <- mean(appSalesData$RATING2)

meanPriceApp3 <- mean(appSalesData$REGPR3)
meanFeatApp3 <- mean(appSalesData$FEAT3)
meanSalesApp3 <- mean(appSalesData$UNITS3)
meanRatingApp3 <- mean(appSalesData$RATING3)
```

##Regression Models

We need to find the variation in sales of each app from the changes in marketimg activity of the competing apps. The marketing activity referes to featuring of the app.

1) Define y (Dependent Variable) which is UNIT(1,2,3).

2) Define X (Independent Variables). In this case, we have X1 and X2 (Regular price, feature)

3) Run the Models. For example, a linear model where Sales (Y) is a function of X1 and X2.

```{r Question 2}
###################################### App 1 ##################################################
#Run the Regression (includes an INTERCEPT)
linearModelApp1 <- lm(UNITS1 ~ REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
semiLogModelApp1 <- lm(LogUNITS1 ~ REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
logLogModelApp1 <- lm(LogUNITS1 ~ LogREGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)

#Results
summary(linearModelApp1)
summary(semiLogModelApp1)
summary(logLogModelApp1)


######################################## App 2 ################################################
#Run the Regression (includes an INTERCEPT)
linearModelApp2 <- lm(UNITS2 ~ REGPR1 + FEAT1 + RATING1 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
semiLogModelApp2 <- lm(LogUNITS2 ~ REGPR1 + FEAT1 + RATING1 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
logLogModelApp2 <- lm(LogUNITS2 ~ LogREGPR1 + FEAT1 + RATING1 + REGPR3 + FEAT3 + RATING3, data = appSalesData)

#Results
summary(linearModelApp2)
summary(semiLogModelApp2)
summary(logLogModelApp2)


######################################## App 3 ################################################
#Run the Regression (includes an INTERCEPT)
linearModelApp3 <- lm(UNITS3 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2, data = appSalesData)
semiLogModelApp3 <- lm(LogUNITS3 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2, data = appSalesData)
logLogModelApp3 <- lm(LogUNITS3 ~ LogREGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2, data = appSalesData)

#Results
summary(linearModelApp3)
summary(semiLogModelApp3)
summary(logLogModelApp3)

```



```{r Question 3}
###Question 3
#Run the Regression (includes an INTERCEPT) - App 1
linearModel_App1 <- lm(UNITS1 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
semiLogModel_App1 <- lm(LogUNITS1 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
logLogModel_App1 <- lm(LogUNITS1 ~ REGPR1 + FEAT1 + RATING1 + LogREGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)

summary(linearModel_App1)
summary(semiLogModel_App1)
summary(logLogModel_App1)

#Linear Model
coeffPrice1_lm_App1 <- (linearModel_App1$coefficients[2])*(meanPriceApp1)/(meanSalesApp1)
coeffFeat1_lm_App1 <- (linearModel_App1$coefficients[3])*(meanFeatApp1)/(meanSalesApp1)
coeffRating1_lm_App1 <- (linearModel_App1$coefficients[4])*(meanFeatApp1)/(meanSalesApp1)
coeffPrice1_lm_App2 <- (linearModel_App1$coefficients[5])*(meanPriceApp2)/(meanSalesApp1)
coeffFeat1_lm_App2 <- (linearModel_App1$coefficients[6])*(meanFeatApp2)/(meanSalesApp1)
coeffRating1_lm_App2 <- (linearModel_App1$coefficients[7])*(meanFeatApp2)/(meanSalesApp1)
coeffPrice1_lm_App3 <- (linearModel_App1$coefficients[8])*(meanPriceApp3)/(meanSalesApp1)
coeffFeat1_lm_App3 <- (linearModel_App1$coefficients[9])*(meanFeatApp3)/(meanSalesApp1)
coeffRating1_lm_App3 <- (linearModel_App1$coefficients[10])*(meanFeatApp3)/(meanSalesApp1)

#Semi-Log Model
coeffPrice1_semi_App1 <- (semiLogModel_App1$coefficients[2])*(meanPriceApp1)
coeffFeat1_semi_App1 <- (semiLogModel_App1$coefficients[3])*(meanFeatApp1)
coeffRating1_semi_App1 <- (semiLogModel_App1$coefficients[4])*(meanRatingApp1)
coeffPrice1_semi_App2 <- (semiLogModel_App1$coefficients[5])*(meanPriceApp2)
coeffFeat1_semi_App2 <- (semiLogModel_App1$coefficients[6])*(meanFeatApp2)
coeffRating1_semi_App2 <- (semiLogModel_App1$coefficients[7])*(meanRatingApp2)
coeffPrice1_semi_App3 <- (semiLogModel_App1$coefficients[8])*(meanPriceApp3)
coeffFeat1_semi_App3 <- (semiLogModel_App1$coefficients[9])*(meanFeatApp3)
coeffRating1_semi_App3 <- (semiLogModel_App1$coefficients[10])*(meanRatingApp3)


#Run the Regression (includes an INTERCEPT) - App 2
linearModel_App2 <- lm(UNITS2 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
semiLogModel_App2 <- lm(LogUNITS2 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
logLogModel_App2 <- lm(LogUNITS2 ~ REGPR1 + FEAT1 + RATING1 + LogREGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)

summary(linearModel_App2)
summary(semiLogModel_App2)
summary(logLogModel_App2)

#Linear Model
coeffPrice2_lm_App1 <- (linearModel_App2$coefficients[2])*(meanPriceApp1)/(meanSalesApp2)
coeffFeat2_lm_App1 <- (linearModel_App2$coefficients[3])*(meanFeatApp1)/(meanSalesApp2)
coeffRating2_lm_App1 <- (linearModel_App2$coefficients[4])*(meanFeatApp1)/(meanSalesApp2)
coeffPrice2_lm_App2 <- (linearModel_App2$coefficients[5])*(meanPriceApp2)/(meanSalesApp2)
coeffFeat2_lm_App2 <- (linearModel_App2$coefficients[6])*(meanFeatApp2)/(meanSalesApp2)
coeffRating2_lm_App2 <- (linearModel_App2$coefficients[7])*(meanFeatApp2)/(meanSalesApp2)
coeffPrice2_lm_App3 <- (linearModel_App2$coefficients[8])*(meanPriceApp3)/(meanSalesApp2)
coeffFeat2_lm_App3 <- (linearModel_App2$coefficients[9])*(meanFeatApp3)/(meanSalesApp2)
coeffRating2_lm_App3 <- (linearModel_App2$coefficients[10])*(meanFeatApp3)/(meanSalesApp2)

#Semi-Log Model
coeffPrice2_semi_App1 <- (semiLogModel_App2$coefficients[2])*(meanPriceApp1)
coeffFeat2_semi_App1 <- (semiLogModel_App2$coefficients[3])*(meanFeatApp1)
coeffRating2_semi_App1 <- (semiLogModel_App2$coefficients[4])*(meanRatingApp1)
coeffPrice2_semi_App2 <- (semiLogModel_App2$coefficients[5])*(meanPriceApp2)
coeffFeat2_semi_App2 <- (semiLogModel_App2$coefficients[6])*(meanFeatApp2)
coeffRating2_semi_App2 <- (semiLogModel_App2$coefficients[7])*(meanRatingApp2)
coeffPrice2_semi_App3 <- (semiLogModel_App2$coefficients[8])*(meanPriceApp3)
coeffFeat2_semi_App3 <- (semiLogModel_App2$coefficients[9])*(meanFeatApp3)
coeffRating2_semi_App3 <- (semiLogModel_App2$coefficients[10])*(meanRatingApp3)



#Run the Regression (includes an INTERCEPT) - App 3
linearModel_App3 <- lm(UNITS3 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
semiLogModel_App3 <- lm(LogUNITS3 ~ REGPR1 + FEAT1 + RATING1 + REGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)
logLogModel_App3 <- lm(LogUNITS3 ~ REGPR1 + FEAT1 + RATING1 + LogREGPR2 + FEAT2 + RATING2 + REGPR3 + FEAT3 + RATING3, data = appSalesData)

summary(linearModel_App3)
summary(semiLogModel_App3)
summary(logLogModel_App3)

#Linear Model
coeffPrice3_lm_App1 <- (linearModel_App3$coefficients[2])*(meanPriceApp1)/(meanSalesApp3)
coeffFeat3_lm_App1 <- (linearModel_App3$coefficients[3])*(meanFeatApp1)/(meanSalesApp3)
coeffRating3_lm_App1 <- (linearModel_App3$coefficients[4])*(meanFeatApp1)/(meanSalesApp3)
coeffPrice3_lm_App2 <- (linearModel_App3$coefficients[5])*(meanPriceApp2)/(meanSalesApp3)
coeffFeat3_lm_App2 <- (linearModel_App3$coefficients[6])*(meanFeatApp2)/(meanSalesApp3)
coeffRating3_lm_App2 <- (linearModel_App3$coefficients[7])*(meanFeatApp2)/(meanSalesApp3)
coeffPrice3_lm_App3 <- (linearModel_App3$coefficients[8])*(meanPriceApp3)/(meanSalesApp3)
coeffFeat3_lm_App3 <- (linearModel_App3$coefficients[9])*(meanFeatApp3)/(meanSalesApp3)
coeffRating3_lm_App3 <- (linearModel_App3$coefficients[10])*(meanFeatApp3)/(meanSalesApp3)

#Semi-Log Model
coeffPrice3_semi_App1 <- (semiLogModel_App3$coefficients[2])*(meanPriceApp1)
coeffFeat3_semi_App1 <- (semiLogModel_App3$coefficients[3])*(meanFeatApp1)
coeffRating3_semi_App1 <- (semiLogModel_App3$coefficients[4])*(meanRatingApp1)
coeffPrice3_semi_App2 <- (semiLogModel_App3$coefficients[5])*(meanPriceApp2)
coeffFeat3_semi_App2 <- (semiLogModel_App3$coefficients[6])*(meanFeatApp2)
coeffRating3_semi_App2 <- (semiLogModel_App3$coefficients[7])*(meanRatingApp2)
coeffPrice3_semi_App3 <- (semiLogModel_App3$coefficients[8])*(meanPriceApp3)
coeffFeat3_semi_App3 <- (semiLogModel_App3$coefficients[9])*(meanFeatApp3)
coeffRating3_semi_App3 <- (semiLogModel_App3$coefficients[10])*(meanRatingApp3)

```