---
title: "Ex6_Team3"
author: "Naga Soundari Balamurugan"
date: "November 13, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
#Required libraries
library(dplyr)
library(gmodels)

source("RFM_Functions.R")
```


```{r read data}
tuscan_data <- read.csv("Tuscan_RFM_Data_R.csv")
liftGainData <- read.csv("Lifts_and_Gain_Data_R.csv")

colnames(liftGainData) <- c("RFM", "Customers", "Buyers")
liftGainData = liftGainData[,1:3]

liftGainData$ResponseRate <- liftGainData$Buyers/liftGainData$Customers

```


# Part I:  Preliminary and Quintile Analysis (Independent RFM)

## 1.	What percent of customers responded (i.e. bought anything) from this catalog?

```{r percent bought}
total_no_customers <- nrow(tuscan_data)
responded_customers <- tuscan_data %>% filter(buyer == 1)
no_res_customers <- nrow(responded_customers)

percent_responded <- (no_res_customers/total_no_customers) * 100
percent_responded
```

>The percent of customer who responded from the catalog is 2.4556%

## 2.	Of those who bought, what was the average dollars ordered from this catalog? 

```{r avg dollar}
avg_dollar <- mean(responded_customers$dollars)
avg_dollar
```

>Average dollars ordered from the catalog is $104.2429.

## 3.	Create quintile (i.e., split by 5) RFM scores for recency, frequency and monetary.

```{r RFM score}
data_rfm <- data.frame(ID = tuscan_data$ID, Recency = tuscan_data$last, 
                       Frequency = tuscan_data$numords, Monetary = tuscan_data$totdol)
RFM_score <- getIndependentScore(data_rfm)
```

## 4.	Create a bar chart showing the response rate (i.e., the proportion of customers who bought something) by recency quintile.

```{r recency}
# Need to sort RFM.score by Customer ID
# Note that tuscan_data is sorted by ID!
sortedRFM <- RFM_score[order(RFM_score$ID),] 


# Crosstab of Recency Score vs. Buyer (did or did not buy offer)
data_crosstab_Recency <- CrossTable(sortedRFM$R_Score, tuscan_data$buyer, prop.r = TRUE,
      prop.c = FALSE, prop.t = FALSE, prop.chisq = FALSE, dnn = c("Recency", "Response"))

# Bar Plot
barplot(data_crosstab_Recency$prop.row[,2], main="Response rate", 
  	xlab="Recency Segments")
```

## 5.	Create a bar chart showing the response rate by frequency quintile.

```{r frequency}
# Crosstab of Recency Score vs. Buyer (did or did not buy offer)
data_crosstab_Frequency <- CrossTable(sortedRFM$F_Score, tuscan_data$buyer, prop.r = TRUE,
      prop.c = FALSE, prop.t = FALSE, prop.chisq = FALSE, dnn = c("Frequency", "Response"))

# Bar Plot
barplot(data_crosstab_Frequency$prop.row[,2], main="Response rate", 
  	xlab="Frequency Segments")
```

## 6.	Create a bar chart showing the response rate by monetary quintile.

```{r Monetary}
# Crosstab of Recency Score vs. Buyer (did or did not buy offer)
data_crosstab_Monetary <- CrossTable(sortedRFM$M_Score, tuscan_data$buyer, prop.r = TRUE,
      prop.c = FALSE, prop.t = FALSE, prop.chisq = FALSE, dnn = c("Monetary", "Response"))

# Bar Plot
barplot(data_crosstab_Monetary$prop.row[,2], main="Response rate", 
  	xlab="Monetary Segments")
```

## 7.	What do the above bar charts reveal about the likelihood of response and the size of the order across the different recency, frequency, and monetary quintiles?

> There is no significant difference between the quintiles. The quintiles based on all three factors have a similar response rate. Among all 3 factors, the segment 5 is highest and segment 2 is lowest only with a small difference. Thus, the likelihood of response does not get affected much by these factors.


# Part II:  Profitability Analysis

## 1.	If the firm would mail to all 96,551 customers, please calculate:
### (a) the gross profit in dollars, 
### (b) the gross profit as a % of gross sales, and 
### (c) the return on marketing expenditures (gross profit/cost to mail catalogs) 

```{r}
gross_sales <- sum(responded_customers$dollars)
catalog_cost <- 96551 * 1
COGS <- 0.5 * gross_sales

gross_profit_dollars <- gross_sales - catalog_cost - COGS
gross_profit_dollars

gross_profit_percent <- (gross_profit_dollars/gross_sales) * 100
gross_profit_percent

ret_expenditure <- gross_profit_dollars/catalog_cost
ret_expenditure
```

> Gross profit in dollars - $27029
> Gross profit in percentage - 10.93583%
> Return on marketing expenditures - 0.2799453


## 2.	What is the breakeven response rate?

```{r}
#Breakeven response rate = (Cost of Marketing)/(Selling Price - Wholesale price - expenditure)

profit <- (no_res_customers * avg_dollar) - COGS 

breakeven_res_rate <- (catalog_cost/profit*percent_responded)
breakeven_res_rate
```

>Breakeven response rate - 1.918595%

## 3.	You can use the Data from the Lifts&Gains Excel Sheet provided or you can calculate the segment performance data by yourself (Basically, a cross-tab as discussed in class). Based on this new dataset (Lifts&Gains or your own), please answer the following questions

### Determine which RFM segments have response rates exceeding the breakeven rate. 

```{r}

# data_crosstab_resRate <- CrossTable(sortedRFM$Total_Score, tuscan_data$buyer, prop.r = TRUE,
#       prop.c = FALSE, prop.t = FALSE, prop.chisq = FALSE, dnn = c("RFM Segment", "Response"))
# 
# filteredSegments <- data_crosstab_resRate$prop.row[,2] > 0.0191
# 
# filteredSegmentsDF <- as.data.frame(filteredSegments)
# filteredSegmentsDF$Segment <-  rownames(filteredSegmentsDF)
# 
# goodResRate <- filteredSegmentsDF %>% filter(filteredSegments == TRUE)

filteredSegments <- liftGainData %>% filter(ResponseRate > 0.0191)
filteredSegments
```

### Determine the number of customers belonging to these profitable segments.
### Determine the number of buyers belonging to these profitable segments.

```{r}
cust_count <- sum(filteredSegments$Customers)
buyer_count <- sum(filteredSegments$Buyers)
cust_count
buyer_count
```

>> No of customers belonging to profitable segments: 52544
>> No of buyers belonging to profitable segments: 1758

### What would the 
### (a) the gross profit in dollars, 
###	(b) the gross profit as a % of gross sales, and 
###	(c) the return on marketing expenditures (gross profit/cost to mail catalogs) have been as a result of mailing the catalog only to those customers in the RFM cells with response rates exceeding the breakeven? 

```{r}
gross_revenue_RFM <- avg_dollar * no_res_customers

gross_profit_RFM_dollars <- gross_revenue_RFM - (0.5 * gross_revenue_RFM) - catalog_cost
gross_profit_RFM_dollars

gross_profit_RFM_percent <- gross_profit_RFM_dollars/gross_revenue_RFM
gross_profit_RFM_percent

ret_expenditure_RFM <- gross_profit_RFM_dollars/catalog_cost
ret_expenditure_RFM
```

>Gross profit in dollars for selected RFM segments: $27029
>Gross profit in percentage for selected RFM segments: 10.93583%
>The return on marketing expenditures for selected RFM segments: 0.2799453


### Finally, generate a Lift&Gains chart as discussed in class comparing the RFM model to the no-model scenario. 

```{r}
liftGainData$quintile = floor(liftGainData$RFM/100)
pivot_lift = aggregate(liftGainData[,c('Customers', 'Buyers')], by=list(liftGainData$quintile), FUN=sum)
pivot_lift$cuml_cust = cumsum(pivot_lift$Customers)
pivot_lift$cuml_cust_per = pivot_lift$cuml_cust/pivot_lift$cuml_cust[5]*100
pivot_lift$cuml_buy = cumsum(pivot_lift$Buyers)
pivot_lift$cuml_buy_per = pivot_lift$cuml_buy/pivot_lift$cuml_buy[5]*100
pivot_lift$resrate = pivot_lift$Buyers / pivot_lift$Customers*100
total_resrate = sum(pivot_lift$Buyers)/sum(pivot_lift$Customers)*100
pivot_lift$Lift = pivot_lift$resrate/total_resrate*100  
pivot_lift$gain_per = pivot_lift$Buyers/sum(pivot_lift$Buyers)*100
pivot_lift$gain_per_cum = cumsum(pivot_lift$gain_per)
pivot_lift
```

> Plotting a banana plot

```{r}
options(warn=-1)
plot(pivot_lift$cuml_cust_per, pivot_lift$Lift, xlab = 'Cumulative Customer %', ylab = 'Lifts')
lines(pivot_lift$cuml_cust_per, pivot_lift$Lift, type = 'l')
abline(h = 100, col = "red")
legend("topleft", legend=c("Lift", "No Model"),
       col=c("black", "red"), lty=1:2, cex=0.8)
```


> plot2

```{r}
options(warn=-1)
plot(pivot_lift$gain_per_cum ~ pivot_lift$cuml_cust_per, xlab = 'Cumulative Customer %', ylab = 'Lifts')
lines(pivot_lift$gain_per_cum ~ pivot_lift$cuml_cust_per, type = 'l')

```

